RNAseq aCRY pCRY data dive (separate)

### 2024-10-17 2_A_dive_aCRY_pCRY (separately)/2_A_dive_aCRY_pCRY_sep.Rmd
restart
manuscript figures, new structure, PCA, Counts, Voclanos

---
title: "RNAseq aCRY pCRY data dive (separate)"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
    toc_depth: 2
always_allow_html: true
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file,output_file= 'Readme.md')
        })
---

@@

# Load System
## -R_libraries
```{r r_libraries, echo=FALSE}
library(patchwork)
library(PCAtools)
library(stringr)
library(R.utils)
library(RColorBrewer)
library(sessioninfo)
library(data.table)
library(plyr)
library(tidyverse)
library(tximeta)
library(tximport)
library(curl)
library(AnnotationHub)
library(DESeq2)
library(EnhancedVolcano)
library(pheatmap)
library(writexl)
library(biomaRt)
library(ape)
library(kableExtra)
library(knitr)

@@

@@

## Make results
```{r, eval=TRUE, include=FALSE, echo=FALSE}

>>>>

---
title: "RNAseq aCRY pCRY data dive (separate)"
author: "Kelterborn"
date: "2024-04-19"
output:
  github_document:
    html_preview: false
    toc: true
    toc_depth: 2
always_allow_html: true
editor_options: 
  chunk_output_type: inline
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file,output_file= 'Readme.md')
        })
---

@@

# Load System
## -R_libraries
```{r r_libraries, echo=FALSE}
library(ggExtra)
library(patchwork)
library(PCAtools)
library(stringr)
library(R.utils)
library(RColorBrewer)
library(sessioninfo)
library(data.table)
library(plyr)
library(tidyverse)
library(tximeta)
library(tximport)
library(curl)
library(AnnotationHub)
library(DESeq2)
library(EnhancedVolcano)
library(pheatmap)
library(writexl)
library(biomaRt)
library(ape)
library(kableExtra)
library(knitr)

@@

### -change wrong aCRY sample
```{r correct_acry, eval=TRUE}

gse_acry
mcols(gse_acry)
colData(gse_acry)

colData(gse_acry)[c("aCRYdark1","WTdark1"),]

colData(gse_acry)$Samplename_new <- colData(gse_acry)$clientName
colData(gse_acry)$Samplename_new[colData(gse_acry)$clientName == "aCRYdark1"] <- "WTdark1"
colData(gse_acry)$group[colData(gse_acry)$clientName == "aCRYdark1"] <- "WTdark"
colData(gse_acry)$genotype[colData(gse_acry)$clientName == "aCRYdark1"] <- "WT"
colData(gse_acry)$treatment[colData(gse_acry)$clientName == "aCRYdark1"] <- "dark"
colData(gse_acry)$condition[colData(gse_acry)$clientName == "aCRYdark1"] <- "WT_dark"

colData(gse_acry)$Samplename_new[colData(gse_acry)$clientName == "WTdark1"] <- "aCRYdark1"
colData(gse_acry)$group[colData(gse_acry)$clientName == "WTdark1"] <- "aCRYdark"
colData(gse_acry)$genotype[colData(gse_acry)$clientName == "WTdark1"] <- "acry"
colData(gse_acry)$treatment[colData(gse_acry)$clientName == "WTdark1"] <- "dark"
colData(gse_acry)$condition[colData(gse_acry)$clientName == "WTdark1"] <- "acry_dark"

colData(gse_acry)[c("aCRYdark1","WTdark1"),]

rownames(colData(gse_acry)) <- colData(gse_acry)$Samplename_new

@@

## Make results
```{r results, eval=TRUE, include=FALSE, echo=FALSE}
